Training a Gaming Agent on Brainwaves

### 2020-08-25 review/response.letter.tex

P3, 11 I assume that the “observational human critic” is the player/participant/subject/human observer. This role should be clarified and terminology used consistently.

\vspace{2em}
\begin{quotation}
{\color{blue}
Absolutely.  We preferred to use OHC "observational human critic" to emphasize what the subject is actually doing while using the system.  We clarified this notation at the Introduction and along the manuscript.
}
\end{quotation}
\vspace{2em}

P3, 41 define MNE

\vspace{2em}
\begin{quotation}
{\color{blue}
Historically MNE stands for Minimum Error Estimate, a software package developed in Martinos Center of Harvard University.  Now MNE  is the name of a entire software platform to perform analysis of several type of brain signals like Magnetoencephalograpy and Electroencephalography.  We added a clarification about this on Section II.C.
}
\end{quotation}
\vspace{2em}

@@

Page 6 Fig 10 the text is not legible, it should be improved.

\vspace{2em}
\begin{quotation}
{\color{blue}
This is now Figure 9, we increased the fontsize, added a colormap and included the confusion matrices for all the subjects.
}
\end{quotation}
\vspace{2em}

Page 6, 40
“However, even though this implies that the agent misses frequently that an action taken is wrong, this is not hindering the overall performance and the agent is still learning.”
// Your results show that this is subject dependent

\vspace{2em}
\begin{quotation}
{\color{blue}
Yes, the Reviewer is correct.  We modified this sentence to state more clearly the message that we wanted to convey, which is, that results are completely subject dependent, and that even when many actions should be tagged as "wrong" (triggering an ErrP) only with a few of them accurate, it is enough to train the agent towards the optimal solution.
}
\end{quotation}
\vspace{2em}

@@

P6, 56
Results show that training a classifier with data of one subject, but using it
to classify the events of experiences of another subject does
not lead to an improvement on the performance of the agent.

// could a pre-trained generic classifier provide a better initial state, subsequently trained with observer data to converge more quickly?
Are there differential err potential for up, down, left, right?

\vspace{2em}
\begin{quotation}
{\color{blue}
The statement is absolutely right.  We extended this experience per Reviewer's suggestion and we verified that effectively the only combination of training/testing in the identification of ErrP that produces an improvement on the performance of the agent is the one that uses information from the same subject (check new Figure 7).   We think a generic-classifier to identify ErrP potentials for any subject (i.e. without calibration) is a research goal of the BCI community because this will allow to have more robust, easier to use, with shorter setups  BCI devices (Suller 2012,\textit{Online use of error-related potentials in healthy users and people with severe motor impairment increases performance of a P300-BCI}).  If such a generic pre-trained classifier could be conceived, this simple game can be used to verify if the number of training sessions required is reduced and this will confirm that the pre-trained classifier is helping to do it more quickly.  We didn't verify if the error potential for up, down, left, right per se produces a different error potential, though we verified that in general getting farther from the target (in Manhattan distance) produces a signal which is slightly different from the one that is produced when the gaming agent moves closer to the target.  We added these very interesting lines of further exploration in Section IV.
}
\end{quotation}
\vspace{2em}

@@

Comments to the Author
The following work shows the usage of ErrPs for training a gaming agent using reinforcement learning. Authors attempt different conventional classification approaches, as well as intersubject classification.

\begin{quotation}
{\color{blue}
We appreciate a lot the time dedicated to review our manuscript.
}
\end{quotation}

It is unclear to me the benefit of evaluating single subject to single subject offline classification accuracy. Please elaborate on this.

\begin{quotation}
{\color{blue}
We tested many variants of simple games and we found that only the one proposed here produced a distinctive  ErrP response. The single subject accuracy that is presented on Figure 5(now) shows the level of ErrP single trial identification that we achieved for different subjects (which is low).  We wanted to emphasize the finding that even with such low levels of identification, it was possible for the agent to learn an efficient strategy.  The accuracy obtained in each single subject is representing the ability of the classifier to identify the ErrP response and to produce accurate rewards for the reinforcement learning scheme.
}
\end{quotation}

@@

Since different subjects attained different performance, all combinations of subjects used for training and testing should be inspected for the 1:1 evaluation setup.

\begin{quotation}
{\color{blue}
This is an excellent idea that we now explored with a new experiment.  We showed the results on Figure 7, where a classifier is trained to recognize ErrP signals using the information obtained from one Trainer subject and used to generate rewards for a gaming agent on a different Tester subject.  We added information about this on Section IV.
}
\end{quotation}

Maybe classification accuracy could be reported at different steps (depending on the amount of training data – gradual increasing the number of subjects)

\begin{quotation}
{\color{blue}
The classification accuracy obtained for all subject is now being shown on Figure 5 with ROC curves.  We shown progressively the experiment itself, where after each gaming agent training match, a new Q-Table is generated based on the rewards tagged from the brainwave session.  The agent improves their efficiency by reaching the target in a progressively less number of steps on average for each run session.
}
\end{quotation}

@@

What is the ratio of hit/no hit segments of action (epochs)?

\begin{quotation}
{\color{blue}
The ratio hit/no-hit segments is 50/50, so for each brainwave session match, as the average number of steps is around 100, it will be 50 segments of hit (moving farther from the target) and 50 of no-hit (moving closer).  
}
\end{quotation}

### 2020-08-25 ErrP.tex
Subo la version que finalmente mandamos a ScholarOne.  En 6 meses charlamos.

\author{Bartolomé Francisco, Moreno Juan,  Navas Natalia, Vitali José, \\
Ramele~Rodrigo,~\IEEEmembership{Member,~IEEE,}
        Santos~Juan~Miguel% <-this % stops a space
\thanks{R. Ramele and J.M.Santos are with the Department
of Computer Engineering, Instituto Tecnológico de Buenos Aires(ITBA), Argentina,
e-mail: rramele@itba.edu.ar.}% <-this % stops a space
\thanks{Manuscript received December 9, 2019; revised August 20, 2020.}}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
In this study, we propose a simple game scenario that can be used to trigger a feedback response embedded in Electroencephalographic (EEG) signals of an observation human critic that observes an agent playing a game.  Based on a Reinforcement Learning (RL) model, the gaming agent receives rewards for their actions on the game and learns its optimal policy.  These rewards are obtained by implementing a Brain-Computer Interface (BCI) system that identifies signal components called Error-related Potentials (ErrP), which occur when a person witnesses a recognizable error. We perform an experiment where rewards are obtained from the ErrP signals from observational human critics watching an agent randomly play a game. The agent is iteratively trained by receiving these rewards and updating its policy, improving its overall performance. Our results are expressed in threefold: (i) the structure of a simple grid-based game that can elicit the ErrP signal component; (ii) the verification that low classification accuracy of just above chance level that produces noisy rewards is enough to allow an agent to learn the optimal policy; (iii) collaborative rewards from multiple observational human critics can compensate the lack of accuracy or the limited scope of transfer learning schemes.
\end{abstract}

@@

This phase is divided into a sequence of run sessions and a gaming agent training match.  During the run session, the agent plays 200 matches guided by a specific Q-Table with a 5\% chance of randomly selecting a movement, to reduce deadlocks and loops.  Following the run session, the agent performs a single gaming agent training match.  The gaming agent starts first with a Q-Table initialized with zeros, so the initial policy for the agent is randomized.  For the agent to learn from the feedback generated by the OHC, movement actions are determined by the agent's actions that are taken from one brainwave session match. This allows the Q-Table to be built based on the OHC's feedback from the movements the agent took, which are executed pseudo-randomly while executing the brainwave session.  The previously mentioned feedback is not explicit as it comes from the interpreted brain signal data. This implies that the reward is determined by the OHC's brain activity.

@@

\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{Images/Average_steps/all.eps}
\caption{Average steps using Q-Table trained with brainwave session matches from six different OHCs.}
\label{fig:avg_steps_all}
\end{figure}

@@

Further work will be conducted in order to increase the complexity of the game to allow the possibility that the target position is dynamically changed.  Although we found that the better performing classifier is Logistic Regression, there is room for improvement.  The classifier could be enhanced to recognize the Error Potential~\cite{Iwane2017} more effectively or could be pre-trained to allow higher accuracy~\cite{Spuler2012}.

>>>>

\author{Bartolomé Francisco, Moreno Juan,  Navas Natalia, Vitali José, \\
Ramele~Rodrigo,~\IEEEmembership{Member,~IEEE,}
        Santos~Juan~Miguel% <-this % stops a space
\thanks{R. Ramele and J.M.Santos are with the Department
of Computer Engineering, Instituto Tecnológico de Buenos Aires(ITBA), Argentina,
e-mail: rramele@itba.edu.ar.}% <-this % stops a space
\thanks{Manuscript received December 9, 2019; revised August 25, 2020.}}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
In this study, we propose a simple game scenario that can be used to trigger a feedback response embedded in Electroencephalographic (EEG) signals of an observation human critic that observes an agent playing a game.  Based on a Reinforcement Learning (RL) model, the gaming agent receives rewards for their actions on the game and learns its optimal policy.  These rewards are obtained by implementing a Brain-Computer Interface (BCI) system that identifies signal components called Error-related Potentials (ErrP), which occur when a person witnesses a recognizable error. We perform an experiment where rewards are obtained from the ErrP signals from observational human critics watching an agent playing randomly a game. The agent is iteratively trained by receiving these rewards and updating its policy, improving its overall performance. Our results are expressed in threefold: (i) the structure of a simple grid-based game that can elicit the ErrP signal component; (ii) the verification that low classification accuracy of just above chance level that produces noisy rewards is enough to allow an agent to learn the optimal policy; (iii) collaborative rewards from multiple observational human critics can compensate the lack of accuracy or the limited scope of transfer learning schemes.
\end{abstract}

@@

This phase is divided into a sequence of run sessions and a gaming agent training match.  During the run session, the agent plays 200 matches guided by a specific Q-Table with a 5\% chance of randomly selecting a movement, to reduce deadlocks and loops.  Following the run session, the agent performs a single gaming agent training match.  The gaming agent starts first with a Q-Table initialized with zeros, so the initial policy for the agent is randomized.  For the agent to learn from the feedback generated by the OHC, movement actions are determined by the reply of the agent's actions that were taken during one brainwave session match, in an offline reinforcement learning scheme~\cite{Levine2020}. This allows the Q-Table to be built based on the OHC's feedback from the movements the agent took, which were executed pseudo-randomly during the brainwave session.  The previously mentioned feedback is not explicit as it comes from the interpreted brain signal data. This implies that the reward is determined by the OHC's brain activity.

@@

\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{Images/Average_steps/all.eps}
\caption{Average steps using Q-Table trained with brainwave session matches from six different OHCs. X axis show the progressive number of gaming agent training matches used to train the Q-Table.}
\label{fig:avg_steps_all}
\end{figure}

@@

Further work will be conducted in order to increase the complexity of the game to allow the possibility that the target position is dynamically changed.  Although we found that the best performing classifier is Logistic Regression, there is room for improvement.  The classifier could be enhanced to recognize the Error Potential~\cite{Iwane2017} more effectively or could be pre-trained to allow higher accuracy~\cite{Spuler2012}.
